
%-------------------------------------
\section{Professional Experience}
%-------------------------------------
\begin{entrylist}
  \entry
    {Sep\,24\textemdash{}Feb\,25}
    {Contract Researcher}
    {CSIRO, Hobart, Australia}
    {Ocean transport matrices for investigating marine Carbon Dioxide Removal (mCDR).}

  % \entry
  %   {Aug\,24\textemdash{}Present}
  %   {Adjunct Fellow}
  %   {University of New South Wales, Sydney, Australia}
  %   {Continued collaboration with A/Prof.~Mark Holzer.}

  \entry
    {Oct\,21\textemdash{}Aug\,24}
    {Research Associate}
    {University of New South Wales, Sydney, Australia}
    {Response of the ocean's carbon and oxygen cycles to climate change.}

  \entry
    {Nov\,19\textemdash{}Oct\,21}
    {Postdoctoral Researcher}
    {University of Southern California, Los Angeles, CA, USA}
    {Global marine trace metals and isotopes modelling.}

  \entry
    {Sep\,17\textemdash{}Sep\,19}
    {Postdoctoral Research Scholar}
    {University of California, Irvine, CA, USA}
    {New tools for improving global biogeochemistry models.}

  \entry
    {Mar\,17\textemdash{}Aug\,17}
    {Casual Research Assistant}
    {University of New South Wales, Sydney, Australia}
    {Continued PhD work.}

  \entry
    {Jun\,16\textemdash{}Dec\,16}
    {Mathematics Tutor}
    {University of New South Wales, Sydney, Australia}
    {\emph{Numerical Methods and Statistics}, 2nd year.}

  \entry
    {May\,11\textemdash{}Aug\,12}
    {Proposal Engineer}
    {Degr\'{e}mont, Suez Environnement, Sydney, Australia}
    {Tendering project management for design, construction, maintenance, and operation.}

  \entry
    {Jul\,08\textemdash{}Jun\,09}
    {Forex Trader Assistant}
    {Soci\'{e}t\'{e} G\'{e}n\'{e}rale Investment Banking, Paris, France}
    {MASEF Internship in foreign exchange market (Forex).}

  \entry
    {Apr\,07\textemdash{}Jul\,07}
    {Mathematics Research Intern}
    {\'{E}cole Polytechnique, Palaiseau, France}
    {Mathematics Specialty Internship at the Laurent Schwartz Mathematics Centre. }

  \entry
    {Sep\,04\textemdash{}Feb\,05}
    {IT Intern}
    {Bioforce, Lyon, France}
    {Development of a database to improve communication and management.}

  \entry
    {Jul\,06\textemdash{}Jul\,06}
    {Assembly Line Worker (Internship)}
    {Mecaplast, Monaco}
    {\'Ecole Polytechnique Industrial Placement.}

\end{entrylist}
% TODO add delivery boy summer job


