





%-------------------------------------
\section{Open-source scientific software contributions}
%-------------------------------------
% TODO make these smaller font
\begin{entrylist}
  \entrysoft{Owner}{OceanTransportMatrixBuilder.jl}{\url{https://github.com/TMIP-code/OceanTransportMatrixBuilder.jl}}{A Julia package to build ocean transport matrices from CMIP model output.}
  \entrysoft{Owner}{AIBECS.jl}{\url{https://github.com/JuliaOcean/AIBECS.jl}}{The ideal tool for exploring global marine biogeochemical cycles.}
  \entrysoft{Owner}{GNOM}{\url{https://github.com/MTEL-USC/GNOM}}{An optimized steady-state model of the modern global marine neodymium cycle.}
  \entrysoft{Owner}{F1Method.jl}{\url{https://github.com/briochemc/F1Method.jl}}{Efficient quasi-auto-differentiation of an objective function defined implicitly by the solution of a steady-state problem.}
  \entrysoft{Collaborator}{UnitfulRecipes.jl}{\url{https://github.com/briochemc/UnitfulRecipes.jl}}{Plotting data with units seamlessly in Julia.}
  \entrysoft{Owner}{Inpaintings.jl}{\url{https://github.com/briochemc/Inpaintings.jl}}{Julia version of MATLAB's inpaint\_nans.}
  \entrysoft{Owner}{WorldOceanAtlasTools.jl}{\url{https://github.com/briochemc/WorldOceanAtlasTools.jl}}{Downloading and using data from the World Ocean Atlas (WOA) database.}
  \entrysoft{Owner}{OceanographyCruises.jl}{\url{https://github.com/briochemc/OceanographyCruises.jl}}{An interface for dealing with oceanographic cruises data.}
  \entrysoft{Contributor}{latexdiff}{\url{https://github.com/ftilmann/latexdiff}}{Compares two latex files and marks up significant differences between them.}
  \entrysoft{Contributor}{YAXArrays.jl}{\url{https://github.com/JuliaDataCubes/YAXArrays.jl}}{Yet Another XArray-like Julia package.}
  \entrysoft{Contributor}{cmap}{\url{https://github.com/tsipkens/cmap}}{Perceptually uniform colormaps for MATLAB, compiled from multiple sources.}
  \entrysoft{Contributor}{Makie.jl}{\url{https://github.com/MakieOrg/Makie.jl}}{Interactive data visualisations and plotting in Julia.}
  \entrysoft{Contributor}{offsetaxis-pkg}{\url{https://github.com/kakearney/offsetaxis-pkg}}{OFFSETAXIS Add an x- or y-axis offset from the plotted axis area (MATLAB).}
  \entrysoft{Contributor}{GeoStats.jl}{\url{https://github.com/JuliaEarth/GeoStats.jl}}{Comprehensive framework for geostatistics (or spatial statistics).}
  \entrysoft{Owner}{OceanGrids.jl}{\url{https://github.com/briochemc/OceanGrids.jl}}{Standard format of grids for AIBECS.}
  \entrysoft{Owner}{OceanBasins.jl}{\url{https://github.com/briochemc/OceanBasins.jl}}{Programmatically determine which ocean basin a (lat,lon) coordinate is in.}
  \entrysoft{Owner}{GEOTRACES.jl}{\url{https://github.com/briochemc/GEOTRACES.jl}}{A package for reading and using GEOTRACES data in Julia.}
  \entrysoft{Collaborator}{HyperDualNumbers.jl}{\url{https://github.com/JuliaDiff/HyperDualNumbers.jl}}{Julia implementation of HyperDualNumbers.}
  \entrysoft{Owner}{DualMatrixTools.jl}{\url{https://github.com/briochemc/DualMatrixTools.jl}}{Efficiently solve dual-valued linear systems.}
  \entrysoft{Owner}{HyperDualMatrixTools.jl}{\url{https://github.com/briochemc/HyperDualMatrixTools.jl}}{Efficiently solve hyperdual-valued linear systems.}
  \entrysoft{Owner}{BlockDiagonalFactors.jl}{\url{https://github.com/briochemc/BlockDiagonalFactors.jl}}{Efficiently solve linear block-diagonal systems with repeated blocks.}
  \entrysoft{Contributor}{Plots.jl}{\url{https://github.com/JuliaPlots/Plots.jl}}{Powerful convenience for Julia visualisations and data analysis.}
  \entrysoft{Contributor}{Unitful.jl}{\url{https://github.com/PainterQubits/Unitful.jl}}{Julia package for physical units.}
  \entrysoft{Contributor}{UnitfulMoles.jl}{\url{https://github.com/briochemc/UnitfulMoles.jl}}{A set of predefined conventional elemental mol units.}
  \entrysoft{Contributor}{Distributions.jl}{\url{https://github.com/JuliaStats/Distributions.jl}}{A Julia package for probability distributions and associated functions.}
  \entrysoft{Contributor}{DiffEqBase.jl}{\url{https://github.com/SciML/DiffEqBase.jl}}{DiffEqBase.jl is a component package in the DiffEq ecosystem.}
  \entrysoft{Contributor}{SciMLBase.jl}{\url{https://github.com/SciML/SciMLBase.jl}}{The Base interface of the SciML ecosystem.}
  \entrysoft{Contributor}{DiffEqOperators.jl}{\url{https://github.com/SciML/DiffEqOperators.jl}}{Linear operators for discretizations of differential equations and scientific machine learning (SciML).}
  \entrysoft{Contributor}{Interpolations.jl}{\url{https://github.com/JuliaMath/Interpolations.jl}}{Fast, continuous interpolation of discrete datasets in Julia.}
  \entrysoft{Contributor}{RecipesBase.jl}{\url{https://github.com/JuliaPlots/RecipesBase.jl}}{Base package for defining transformation recipes on user types for Plots.jl}
  \entrysoft{Contributor}{CMAP.jl}{\url{https://github.com/simonscmap/CMAP.jl}}{Simons CMAP Julia client.}
  \entrysoft{Contributor}{InverseDistanceWeighting.jl}{\url{https://github.com/juliohm/InverseDistanceWeighting.jl}}{Inverse distance estimation solver for the GeoStats.jl framework.}
  \entrysoft{Owner}{Earth2014.jl}{\url{https://github.com/briochemc/Earth2014.jl}}{Download topographic data for the globe.}
\end{entrylist}

